### 2020-01-02 Literature Review/Literature Review - Revised/sections/MARL.tex
Added Revised Literature Review

\maketitle

\tableofcontents

\chapter*{Introduction}

The areas of interest regarding Multi Agent Systems fall into two
distinct categories (which have some slight overlap). The first is
denoted as 'Decision Making', though the terms 'Planning' and
'Distributed Control' may sometimes be used as substitutes. It is
important to note that, in my case, I do not include Planning
Formalisation techniques such as PDDL. Instead, I focus on the
particular methods which involve interaction in the world. The second,
I will refer to as 'Multi Agent Dynamics', though sometimes I will
refer to this as 'Stability Analysis'.

\subsection*{Scope}

Both of the aforementioned topics have been applied to all variants of
multi agent systems and have sufficient room for further
exploration. The typical variants of multi agent systems that I will
consider are

\begin{enumerate} \item Swarms \item Multi Agent Reinforcement Learning (MARL) \item Decentralised
Partially Observed Markov Decision Processes (Dec-POMDP) \item Game Theoretic Approaches \item Hard
Coded \end{enumerate}

In the above, 'Game Theoretic Approaches' cover a wide spectrum,
including zero-sum (minimax) games, bayesian games, and many more. The
final category, 'Hard Coded', refers to any approach which does not
fit neatly into any of these categories. The name is chosen since they
often refer to methods which revolve around a series of if-else
statements.

\fr{Is 'Hard Coded' the terms also used in this literature, or is it your own?}

I will first consider Decision Making as this is most closely related
to the research proposal, before I consider Multi Agent Dynamics,
which has strong implications for Safe and Trusted Multi Agent
Systems.

\subsection*{Objectives}

The aim of the following sections is not to provide an exhaustive list of all work done in the
aforementioned areas. To attempt to do this would be an exercise in futility. Instead, it is to
identify research directions which lie within the broad scope of Multi-Agent Systems (MAS). With
these directions, we may be able to narrow down the remaining literature review and hone in on
particular problems and, in fact, we may find that we address multiple of these over the next four
years (while we, of course add more). As such, the end of each chapter will provide a list of
research directions which I have identified from the preceding review.

\chapter{Decision Making}

Decision making refers to the generalised problem of considering how a multi-agent system should
interact in the world to achieve their goals. This subsumes both the cases where the agents' goals
are aligned (cooperative) or in conflict with one another (competitive).

The following sections will provide an overview of the literature aimed towards coordinating such
systems as followed by interesting sub-fields in each approach which present avenues for research
related to Safe and Trusted AI (STAI). These, of course, are not exhaustive and more will be added
as the review progresses.

\section{Swarms}

Swarm based systems comprise of multiple homogeneous agents which are able to organise themselves
through a formation using a series of simple local interactions with their neighbours
\cite{Couceiro2015}. Whilst the individual agents are generally simplistic, the collective behaviour
may exhibit complex phenomena emulating systems observed in biological organisations such as bee or
ant colonies \cite{Sethi2017}. Hybrid algorithms such as in \cite{Gao2018} show an accelerated
performance in reaching globally optimal solutions in search-based tasks. The advantage of many
swarm algorithms is that they are based on local interactions and so are incredibly scalable
\cite{Rizk2018}.

The reduction of the complexity in interactions between agents also allows for the robots to perform
other calculations on board. In \cite{Pini2011TaskSelection}, Pini et al. leverage this by
considering adaptive task partitioning across swarms. This allows a swarm, in a decentralised
manner, to deliberate whether to partition a task into its sub-tasks or to perform the task in its
whole. As of now (to the best of my knowledge) the problem of partitioning general tasks into its N
sub-tasks is unexplored. This, however, highlights another advantage of swarm systems; they are
readily divided into sub-groups (as in \cite{Zahadat2016DivisionInhibition}) to perform a
divide-et-impera (divide and conquer) approach to solving problems \cite{Pini2011TaskSelection}).

Furthermore, swarm systems may be designed in a leaderless manner and so do not require the use of a
central controller \cite{Couceiro2015}. This presents the advantage that the system can rapidly
adapt to the loss of agents or separation of groups throughout the task. However, the assumptions
made regarding the homogeneity of individual agents and the simplicity of their local interactions
result in significant limitations placed on the complexity of the tasks that swarm systems can
accomplish.

\fr{What are the standard techniques used in swarms? that is, how are swarms and their interactions modelled? how are solutions computed? what kind of algorithms are used in this area? most importantly, does any of these overlap with any of the areas below, for example (PO)MDPs?}

\subsection{Co-evolution and Self-Healing}

Recently, there has been an increased interest in introducing
heterogeneity into the swarm systems to improve their real world
applicability. An example of this which have been shown strong real
world success can be found in
\cite{DucatelleSelf-organizedSwarms}. Here, the authors consider two
swarm teams, referred to as 'foot bots' and 'eye bots' who work in
unison to explore an environment and solve a navigation task.

This area of research is sparsely populated and warrants further
exploration. This is since the use of co-evolutionary teams can
improve the robustness of the swarm optimisation. This is since it
will be possible for a team to automatically determine when robots in
the other team are not exhibiting expected behaviour and ensure that
the other team self corrects. This process is referred to as
'Self-Healing' in \cite{LiuTrust-Aware}. Here, the authors allow a
user to define the goals of a swarm system. From this, a 'trust'
metric can be defined which measures the deviation of each agent from
the expected behaviour. The self-healing process occurs by limiting
communication of all agents with 'untrusted' agents and encouraging
communication with 'trusted' agents. The unison of self-healing with
co-evolution may present the opportunity for heterogenous swarms to
maintain their evolutionary stability, even in the face of
environmental disturbances.

\subsection{Fault Detection}

The above sections have considered the fact that swarm systems are
robust to losses in the group.  However, any MAS system must first be
able to recognise that an agent has undergone some failure.

To this end, Tarapore et al. \cite{Tarapore2019FaultDetection} develop
a robust fault detection approach in which the swarm itself, in a
decentralised manner, is capable of assessing deviation from 'normal'
behaviour, even when the behaviour of the swarm itself is altered
(perhaps by a remote operator). The authors achieve this by requiring
that the agents themselves sense and characterise their own
behaviour. This characterisation is formulated as a binary feature
vector which is then communicated to the agent's neighbours. These
neighbours will reach a consensus over whether the agent should be
treated as faulty based on their collective behaviour. The results
presented in \cite{Tarapore2019FaultDetection} show extremely
promising results and suggest that their method is, in fact, able to
determine faults with high accuracy in the presence of various fault
types (including sensor and actuator failures), although poor
performance is seen in actuation failures in some instances. It should
be noted that this method requires that each robot transmit their
feature vector to the nearest neighbours. In environments where
communication may be severely limited, this may present further
errors. Furthermore, it is unlikely that, when a robot is damaged,
only one of its components will be affected. Therefore, it is
important to determine the effect on performance in the face of
multiple agent failures and in communication losses. This exploration
may open the possibility of improving the state of the art in terms of
failure detection in swarm systems. (Of course, this conclusion is
based off two papers so further review is required).

\fr{Fault detection and fault recovery (D\&R) is one of the themes that encompasse several different research areas. As such, it would be interesting to check whether the techniques applied to Fault D\&R can be successfully exported from one area to another. However, this depends essentially on the different modelling assumptions.}

\subsection{Verification}

Both of Alessio's papers \cite{Kouvaros2019FormalSystems, Lomuscio2019ASystems} fit in here but they
require further reading

\subsection{Directions}

From the above consideration of swarms, the following research
directions have been identified which, in my view, concern themselves
with STAI.

\begin{enumerate} \item Healing through co-evolution: The application of heterogenous robot swarms
towards ensuring that emergent phenomenon and swarm behaviour are as
expected by the user.

\item Fault Detection in limited communication:
Considering the ability of a swarm to, in a decentralised approach,
consider which robots in the team have failed, even in cases of no
communication or multiple failures.

\fr{The second item looks promising, possibly in combinations with
  techniques from Game Theory and MARL. Let's keep Fault R\&D in
  mind.}

\end{enumerate}

\section{Dec-POMDPs}

The use of POMDPs in multi-agent settings is formalised as
decentralised POMDP (Dec-POMDP) which aims for a team of agents to
maximise a common utility. However, it has been found that determining
the exact solution to Dec-POMDP problems is NEXP \cite{Eker2011} and
so is intractable for all but toy problems. A number of methods have
been presented to attempt to solve Dec-POMDPs. Oliehoek gives a review
of these in \cite{OliehoekDecentralizedPOMDPs}. Most solutions (such
as brute force) are intractable for all but toy problems.

Approximate solutions to Dec-POMDP have been proposed, perhaps most
notable of which is the proposal of MacDec-POMDP \cite{Amato2015} by
Amato et al. Here, macro actions (actions which extend over multiple
time steps) are used, as opposed to low-level actions which are
re-evaluated at each time step. This allows an exact solution to be
found as it does not need to be evaluated at each time step. This
method assumes that, once macro-actions are distributed, the policies
(sequence of state-action pairs) are known. Since this is not the
case, Amato also proposes the use of a Dec-POSMDP
\cite{Amato2017Decision-MakingLearning}, where 'SMDP' refers to
'Semi-Markov Decision Process, in which a high level model is defined
without the underlying Dec-POMDP's actions and observations.

However, this is largely applicable in passive settings where common
payoffs can be determined by an offline planner. They also require a
significant amount of data with which to allow the system to learn the
underlying models and payoff structures. This limits the applicability
of the system when communication is limited and the system is
presented with environments that it has not seen before.  Recent work
in MDPs \cite{Klima2019RobustDomains} has considered learning in the
face of Significant Rare Events (SREs) which the system has not yet
observed. Currently, it is required that a model of such SREs is known
and so it would be interesting to consider the application of
Dec-POMDPs in situations where the SRE model is incomplete or
erroneous and assess the robustness of the Dec-POMDP framework against
such events.

\subsection{Directions}

The area of Dec-POMDPs still requires more review from me, especially for solutions which are not
developed by Amato as he seems to largely dominate the field. Based on this initial review of the
area, a potential direction for research is

\begin{enumerate} \item Significant Rare Events: Consider Dec-POMDP capability to remain robust to
  SREs which have a limited or erroneous model.

\item Agent Failures: The Dec-POMDP model uses a
centralised planner which acts offline. It therefore assumes that the agents will be able to carry
out their assigned tasks. It would be interesting to examine the possibility of, either adaptive
planning, or planning with contingencies in the Dec-POMDP framework. \end{enumerate}

\fr{It looks like this second point is related to Fault R\&D discussed above. It might be worth to make a comparison and see what are the general results in the two areas.\\
Also, it might be interesting to understand why swarms scale up better
than MDPs, and in general why the former have better computational
properties than the latter: is it a matter of
``homogeneity''? Then, what about considering ``homogeneous'' MDPs, or
some other swarm-like restriction? It might be interesting to combine
the two approaches in order to get the ``best of both worlds''.}

\section{Game Theoretic Approaches}

Game theoretic models are generally the go-to method for understanding
multi-agent systems. As such they fit into all of the categories in
this chapter (except, perhaps, swarms) since Dec-POMDP and MARL
methods have both used game theory to support their frameworks. In
fact, Dec-POMDP is a subset of Partially Observed Stochastic Games
(POSG), in which all agents use the same payoff. \fr{That's an
  interesting remark. It might be worth to check whether we can
  leverage on this and similar observations.} Game theory can,
therefore, be used in an applied capacity to direct task allocation
across heterogenous teams.

\subsection{Market Based Methods}

Garapati et al. \cite{Garapati2018AMissions} define a market based
method as the setting where agents "follow their own interests and
establish the mechanism of a market for distributing the
tasks". Auctioning is the most widely used sub-field of market
approaches and so I will use them interchangeably.

Whilst there are different variants to autioning, the general
procedure is that an auctioneer who has knowledge of a task (or
multiple tasks) will set up an auction for said task. Agents can then
make bids on these tasks and, once the auction is complete, the
highest bid will win the task. In the specific application to
robotics, a robot's bid will often reflect the costs, suitability or
utility their undertaking the task
\cite{BernardineDias2006Market-basedAnalysis}. This immediately
highlights a few points. The first is that the method is not too
heavily reliant upon a single processor to determine some joint
policy. Tasks are allocated on a case-by-case basis and the utilities
are calculated by the agent themselves. The only centralised process
is the auctioneer's assessment of the winner which then relays this
information back to them. The downside of this is that the system is
heavily reliant upon strong communication channels, without which
tasks may not be assigned, incorrect utilities may be communicated
and, in general, sub-optimal solutions reached.  Furthermore, the
requirement that the agents themselves determine the cost of their
actions assumes that they have the computational capability to do
so. Furthermore, the bids placed by each agent need to be a strong
representation of their capability to perform a task which may be hard
to estimate without expert knowledge. However, market based methods
are well suited to explanation through argumentation (similar to
\cite{Jung2001DistributedArgumentation}.

\fr{The game-theoretic approaches described above might suffer from the
  same drawbacks identified above for fault detection, namely reliance
  on communication and on a single central authority. I'd rather
  favour distributed approaches. Also, market-based mechanisms and
  negotiation might lead us to a completely different direction.}

With well chosen payoffs, market based approaches work extremely
well. For instance, in \cite{Dias2000ASystem}, the authors show that a
free market approach (where agents try to maximise their own profits)
can lead to a strong collaborative effort across teams. Similarly, in
\cite{Thomas2005Multi-robotScenarios}, Thomas et al. apply the
auctioning scheme presented in \cite{Gerkey2002Sold:Coordination}
towards a robot construction team. However, it is important to note
that these are both passive settings; tasks were assigned before the
team were in the field and, in the case of
\cite{Gerkey2002Sold:Coordination}, the system would repeat the
bidding process if a robot failed. While both show strong performance,
it cannot be said that either would be applicable in dangerous
environments in which dynamic reassignment must happen within strict
time constraints. Stancliff et
al. \cite{Stancliff2009PlanningAllocation} suggest that a more robust
method to planning would be to account for failures a priori, a
philosophy which is exemplified in \cite{Chen2010ACollaboration} who
consider the robot's reliability and relevance to a task as well as
'history relevance' which considers the relationship between pairs of
robots with the aim of producing more effective teams.

There has also been some interesting work in probabilistic
verification of market based approaches.  Most notable to me is
\cite{Pallottino2007ProbabilisticAvoidance} which considers the case
of conflict avoidance. Though their method focuses on collision
avoidance, it highlights the need for verification of conflict
resolution and goal achievement in market based approaches with
different payoff structures. Sirigineedi et
al. \cite{Sirigineedi2010DecentralisedApproach} make a step in this
direction by considering the verification of cooperative surveillance
along a route network.  From my understanding, this means that they
were able to verify that their agents were able to traverse along the
network without interference. However, this, as always, requires
further analysis to truly understand.

\subsection{Directions}

The particular considerations which have jumped out to me from the above analysis are as follows:

\begin{enumerate} 
	\item Verification of goal achievement under different payoffs: can we ensure that
	self-interested agents will, in fact, show cooperative emergent properties? A similar question
	arises in terms of valuations (how much cost each agent incurs). 
	\item A priori consideration of
	reliability: Can we learn and take into account the fact that robots may fail throughout the
	progress of a mission when we assign tasks? 
\end{enumerate}

\subsection*{Stochastic Games}

\section{Hard Coded}

\section{MARL}

Reinforcement learning extends the Markov Decision Process problem by
considering the case where the payoff model is not known. This, of
course, is the case for most real world environments. As such, MARL
algorithms can perhaps be considered to be more applicable than
Dec-POMDP models.
\fr{Why would it be so? after all, also MARL assumes a certain pay-off structure.}

Fortunately, MARL has picked up a lot of traction in
research recently, with a large body dedicated towards solving the
many problems it presents.

The largest problem in MARL is the non-stationarity of the environment \cite{Hernandez-LealA}. In
single-agent settings, it is assumed that the environment is Markovian. However, this must be lifted
in the Multi Agent setting since other agents in the environment will be learning concurrently. This
learning will be based on their own history of interactions which extend beyond the previous state.
As such, we must now consider that the policy for any one agent will depend on the policy of all
other agents. As such, a big concern in this area is regarding convergence guarantees and the
stability of the learner system. Approaches to this will be discussed in the next chapter.

@@

\subsection{Directions}

I still have a lot of reading to do regarding MARL, which, in turn, will identify new directions.
However, on initial assessment I put forward

\begin{enumerate} \item Modelling evolving teammates: The purpose of this is to more strictly ensure
the stability of the learning process. However, the particular problem I suggest is to consider the
modelling in a decentralised manner and with the consideration of evolving numbers of agents in
teams. \end{enumerate}

\fr{This looks like an interesting, non-trivial problem: how can we
  represent the other agents within the agent model itself, in order
  to improve learning in MARL? Shall we have a closer look at this problem?}

\section{MARL Approaches} \label{sec::MARL Approaches}

The task of MARL is to determine an optimal joint policy for all agents across the game. This joint
policy may be the concatenation of all the individual policy or it may just be options for each
agent to take. In either case, optimality is defined through the standard notions of Nash equilibria
and so, in this section, I will try to consider the broad spectrum of methods which attempt to
achieve this Nash equilibria. I will start with the more foundational methods which are, thankfully,
all reviewed by Schwartz in  \cite{SchwartzMulti-agentApproach}. I will use the chapters of the book
to help guide this review. I am not referencing the individual papers immediately, though the
references can be found in the book.

\subsubsection*{Learning in Two Player Matrix Games}

@@

\subsubsection*{Learning in Multiplayer Stochastic Games}

\fr{All the above looks extremely interesting. I would explore the
  above for decentralized and partially observable settings. What
  results are mentioned \cite{SchwartzMulti-agentApproach} under such
  assumptions?}

\subsection*{Dec-POMDP and MARL}

As Dec-POMDPs are the theoretical formulation of MARL problems, it stands to reason that other
methods for solving Dec-POMDPs should provide insights into improving MARL. Fortunately Oliehock in
\cite{OliehoekDecentralizedPOMDPs} presents a number of existing methods towards solving Dec-POMDPs.
The methods which I feel may be applicable are  \begin{enumerate} \item Alternating Maximisation: This
is effectively coordinate ascent for determining a joint policy. \item Approximation as Bayesian
Games: Perhaps solving the repeated Bayesian Game through MARL would be more efficient. It does,
however, force us to ask how best to sub-divide a Dec-POMDP into a series of Bayesian Games  \item
Selecting sub-tree policies: Could DL be used to determine which sub-tree policies are optimal? In
order to make this work, we would also need to consider how to select the feature space of sub-trees
and how to collect this information. \end{enumerate}

\chapter{Multi Agent Control}

\section{Stochastic and Robust Model Predictive Control}

The idea of Stochastic Control is best described in the research statement of the Control and
Analysis of Stochastic Systems (CASS) group at Penn State:

\begin{displayquote}
	"...to model, predict and control uncertain engineering systems where the interplay between
	dynamics and uncertainty (stochasticity) is important."
\end{displayquote}

When operating in the real world, systems are subject to uncertainty and environment perturbations.
Despite this, for their safe operation, they must provide certain guarantees (such as collision
avoidance) and remain stable. It is with this in mind that we must design control mechanisms for the
system which satisfy these requirements, even in the face of uncertainty. Methods in stochastic
control have found their way into controlling power distribution, chemical processes and (of course)
robotics.

\subsection*{Model Predictive Control}

Model Predictive Control is a long standing paradigm in AI which looks specifically at the problem
of operating real-world agents safely in the face of environmental disturbances. The overarching
idea begins with the assumpion that we have a model of the environment. As an example, in
the case of autonomous vehicles, we have a model of how adjusting the angle of the front wheels will
affect the heading of the car. We then perform a finite horizon look ahead, in which we estimate the
environment state for a few time steps ahead, and generate a policy for this horizon. The agent
performs the immediate action generated by the policy, and then we repeat the process, after taking
measurements of the environment to determine the error in the system. Throughout this process, the
controller (a.k.a. policy) must remain stable, but also satisfy constraints. From our previous
example, a likely constraint would be that the controller will never result in the car going on the
pavement, where it would present a real hazard to pedestrians. It is through these constraints, and
the requirement of stability that the system is required to remain safe throughout operation. To
that end, mathematical proofs of these properties are provided in the literature ensuring that we
can trust in the system's performance.

Deterministic MPC assumes that the environment is completely deterministic and, therefore, assumes
knowledge of the exact nature of the disturbances. This somewhat naive assumption simplifies
computation and so appears often in the literature, as in \cite{Rosolia2018}. However, it does not
provide strong guarantees outside of games and simulations. Robust MPC brings this to a higher level
of abstraction in which system perturbations, though deterministic, lie on a bounded set. Therefore,
we no longer assume the exact nature of the environment and can guard against worst case scenarios.
This is extremely effective in closed environments or for simple tasks, but falters in more complex
environments.

Stochastic Model Predictive Control (SMPC) lifts the assumption made in MPC, namely that
perturbations are deterministic and lie on a bounded set \cite{Mesbah2016}. To accomplish this, we
define chance constraints, for which probabilistic guarantees must be determined. Furthermore,
optimality is defined in terms of the minimisation of the expectation of a probabilistic
cost function. This formulation brings about controllers which are more applicable and robust when
deployed. However, the field is in its infancy and presents a number of theoretical challenges.
These are best described by Mesbah in \cite{Mesbah2016}

\begin{enumerate}
	\item The arbitrary form of the feedback control laws
	\item The non-convexity and intractability of the chance constraints
	\item The complexity of the uncertainty propagations
	\item Establishing stability of the control problem
\end{enumerate}

Since the review \cite{Mesbah2016} was written in 2016, there have been a number of approaches
towards solving some of these problems, most notably the intractability of the chance contraints.
For instance, in  \cite{Paulson2019}, Paulson and Mesbah propose the use of joint chance constraints
in considering time varying stochastic disturbances as well as model uncertainty. This is shown to
be strongly suited to non-linear systems, which itself is an open problem in the MPC sphere.

The research in using Distributed Predictive Control is quite sparse as compared with, for example,
single agent predictive control. The added complexity of stochastic environments has meant that this
area of research is still very open for looking into. With this said, the main works that I have
found useful whilst reviewing the literature are \cite{Conte2014}, \cite{Christofides2013} and 
\cite{Giulioni2015}. In almost all of the presented methods, a number of assumptions are made.
Usually these are some combination of the following:

\begin{enumerate}
	\item The agents act in a deterministic environment. This suggests that predicted futures will
	be close enough to the ground truth.
	\item The agents are uncoupled from one another. This is a strong assumption to make and
	essentially allows us to consider the agents as completely independent of one another. 
	\item The agents can easily communicate with one another. This allows for longer pieces of
	communication (most often predicted trajectories) to be communicated between agents.
\end{enumerate}

\subsection{Directions}

The problem of MPC, both in the stochastic, and the robust sense, are rife for work in theoretical
and applied problems. Control in autonomous systems is also one of the more applicable problems
related to STAI since it requires that we place mathematical guarantees on the performance and
stability of the system as well as guarantees on the satisfaction of constraints. This is, of
course, an ever present problem in autonomous systems which operate in the real world. I begin by
listing the more theoretical areas for exploration in MPC before then considering their application
domains.

\begin{enumerate}
	\item Significant exploration is required with regards to the optimisation problem. Especially
	for non-linear (or coupled systems), solving the optimisation problem is a struggle. As such,
	approximate methods (such as sampling) should be explored and their effect on the system
	guarantees presented.
	\item Uncertainty propagation in SMPC is also an important problem since we must be able to
	determine the uncertainty in the environment model in order to generate control laws. We should
	consider a comparison of formal techniques, such as Bayesian inference (e.g. Markov models) or
	particle filters, against modern deep learning methods for propagation.
	\item Adaptive MPC is particularly important when considering failures in a system. In his talk,
	Mark Cannon considers the platooning problem (in which multiple autonomous vehicles move
	together whilst maintaining a specified distance from one another). Consider, then, the case
	where one vehicle undergoes a fault (burst tyre etc). The system model must incorporate this,
	and hence requires adaptation. It would again be interesting to consider the use of neural
	networks in this manner. However, specifically we should consider whether the use of a function
	approximator in the form of an NN might result in a violation of the constraints.
	\item Distributed predictive control. This is what, in my view, we could work towards. This is a
	difficult problem due to the coupled nature of the system dynamics. We will need to consider: the
	effect that each agent has on the other, the effect of the environment on all agents, estimating the
	future behaviour of each agent, and ensuring that all agents do not violate the constraints. It is
	here that I believe game-theoretic notions (especially differential games) will come to our
	aid. Similarly, mean-field games should be considered in the general N-agent problem, as well as
	in the case of multiple disturbances, but I will elaborate on this in the applied problems
	section.
\end{enumerate}

the following presents a consideration of the applied end of MPC problems. I have tried to focus on
the domain independent suggestions, since the domain specific ones are virtually limitless.

\begin{enumerate}
	\item Mean-field predictive control. Consider the case of a hybrid system, in which many components
	interact with each other. In addition, we may consider that there are multiple known disturbances
	acting on the system. This, at first seems like an impossible problem to solve due to the many
	interactions between all elements of the system. However, we can consider this as a game
	theoretic problem in which the components and the disturbances are players. The relatively new
	class of 'mean-field games' is a method which allows the many body problem to be approximated as
	a series of two-agent problems \cite{Yang2018}. Whilst the concerns in the 'Distributed
	predictive control' remain, this may prove to be a valuable area of applied research.
	\item Swarm control. Swarms often have simpler control rules implemented within each agent,
	which emerge into more complex results. It would be interesting to consider the application of
	robust and stochastic MPC with the aim of improving swarm results and satisfying constraints of
	the emergent phenomenon. This would be of particular interest in the case where the swarm has to
	track multiple objectives. A prediction of the swarm evolution may prove beneficial to ensure
	that all agents comply with the expected behaviour as the swarm switches tasks. Similarly, an
	adaptive stochastic model would be interesting to examine here to remain robust to agent
	failures in the group.
	\item Modular Robotics?
\end{enumerate}

\fr{All the above looks interesting. However, we need to understand
  how much the scalability issue is going to affect the strength of
  the results we can expect. Is a multi-agent extension of MPC
  completely hopeless? or can we find ``islands of tractability'',
  perhaps in combination with some of the other methods that you
  mention?}

\section*{Multi Agent Dynamics}

Multi Agent Dynamics considers the problem of mathematically modelling learning in Multi Agent
Systems (MAS). This model then serves to be able to predict the evolution of a learning system as
well as to understand the trajectory of learning. Typically, this looks at considering whether or
not the method is likely to converge towards a Nash equilibrium. This is generally a difficult
problem to solve \cite{ShohamMultiagentFoundations} for all but toy problems. To extend this
applicability into real world settings requires the study of stable equilbrium points;
\cite{Letcher2019DifferentiableMechanics} shows that the stable equilbrium and Nash equilibrium (NE)
are not necessarily the same and, in fact, argue that stable points are more informative than NEs.
Stability provides some guarantees against the stochastic nature of the environment since a stable
equilibrium will always be returned to even after perturbations. This extremely important in Safe
and Trusted AI as it provides guarantees against undesired behaviour in real world
environments.

\section{Stability of Learning Agents}

@@

\fr{The above sounds a bit technical, but the interest for MARL is apparent. It might be worth to understand what are the limits of applicability of these resutls, that is, what assumptions are they based on.}

\section{Learning Stable Agents}

The above discussion has considered how notions of stability and control are important to
Multi-Agent Learning. It stands to reason, therefore, that Multi-Agent Learning and, more
specifically, game theory, can be used to develop controllers which drive systems to stable states.
This idea is explored in \cite{Marden2018AnnualControl}. Here, a zero-sum game is considered in
which the players are a controller and an adversarial environment. The design of the controller must
be such that it is able to drive the system to zero error. To illustrate, consider the problem of
designing a controller for a re-entry vehicle, as in \cite{Breitner1994ReentryGame}, in which
vortices seek to destabilise the agent. This will allow us to build stable agents in a much more
efficient manner since we can simulate the adversarial environment and hypothetical scenarios the
agent may encounter without actually encountering them. The same notion is explored by Bardi et al
\cite{Bardi1991DifferentialDisturbances}.

 Mylvaganam et al, in \cite{Mylvaganam2017AutonomousApproach}, consider the N-robot collision
 avoidance problem, similarly from the point of view of differential game theory. They develop a
 robust feedback system for the robots which they show to be able to drive the system towards
 predefined targets whilst providing guarantees of interference from other agents (or lack thereof).
 In \cite{MylvaganamASystems}, Mylvaganam also considers a game theoretic control of multi-agent
 systems in a distributed manner. Here, agents only consider their own payoff structure and have
 limited communication with one another. The author shows that the an approximate equilibrium can be
 found using algebraic methods and illustrate the capabilities of the technique using a collision
 avoidance example. For the sake of brevity, I will not include all of the numerous strides that
 Mylvaganam has introduced to the area. However, I must conclude with those presented in
 \cite{Mylvaganam2014}. Here, the author presents approximate solutions to a number of differential
 games, including linear-quadratic differential games (in which system dynamics are linear functions
 whilst payoff functions are quadratic), Stackelberg differential games, where a hierarchy is
 induced across the players (a notion was suggested in the research proposal) and mean-field games,
 which is discussed in Section \ref{sec::MARL Approaches}. The importance of the linear-quadratic
 differential game is the stability of the solution; solutions for the Nash equilibria are
 admissable iff they are locally exponentially stable (which the author often shows with the aid of
 Lyapunov functions). Approximate solutions to the NE are developed which are more feasible to
 calculate online. The author then shows that this is not simply a theoretical exercise by applying
 the novel methods towards multi-agent collision problems and designs dynamic control laws which
 guarantee that each agent will reach their desired state whilst avoiding collision with the other
 agents. Similarly, the Stackelberg game is applied to the problem of optimal monitoring by a multi
 robot system.

\subsection{Directions}

I will briefly summarise the research directions which I develop in this section, to save ourselves
some time, and to preserve sanity. \textbf{I'll do this later. Sanity is overrated.}

The above discussion has illustrated a few points. The first, and perhaps most important, is that
stability is extremely applicable to Stochastic Optimal Control. This is because of the fact
that learning agents, especially in real world environments, are subject to uncertainty and
perturbations as well as epsilon-random exploration. As such, it is important that the system is
able to return to a stable state after such perturbations. This leads to the need to develop
learning systems as in \cite{Letcher2019DifferentiableMechanics} which are attracted to stable
equilibria. Similarly, it allows us to consider existing algorithms and whether they lead to stable
equilibria. For instance, Letcher et al show in \cite{LetcherSTABLEGAMES} that the Learning with
Opponent Learning Awareness (LOLA) algorithm \cite{Foerster2018LearningAwareness} does not converge
to stable fixed points.

The second point is that the notion of stability has multiple definitions. Each one is appropriate
in different conditions and, as such, it is important to explore stability from various viewpoints
to consider how to best understand the evolution of a learning system.

\fr{I agree that we first need to understand what is exactly meant by
  stabililty across all these different works, and possibly use a
  notion that is relevant and interesting, especially in a multi-agent
  contex as you point you hereafter.}

Another factor to consider is suggested in \cite{Milchtaich2007StaticGames}; multiplayer games do
not necessarily contain stable fixed points. The existence of stable equilibria is therefore an open
question and is well worth consideration. This would help guide the choice of loss functions and
strategy spaces. This is likely to be an extremely difficult problem to generalise but would have a
dramatic impact on the safety certification of MARL systems.

The problem of finding stable solutions through multi agent dynamics also opens the door for a large
degree of application domains which are currently quite sparse. I would recommend looking at the
contents page of \cite{Hamalainen1991DifferentialFinland} which illustrates a number of applications
of dynamic and differential game theory in a number of domains including: pursuit-evasion, systems
control and economic modelling. My particular interest, as always, lies within robotic control
problems. This appears to be the most direct and relevant application of stable MAS systems. An
example of this might be the problem of Cooperative Moving Path Following Control considered by
\cite{Reis2019RobustVehicles}. Here, multiple agents must track moving targets according to a
pre-defined path without interfering with one another. It is clear then that each player's control
is dependent on the other and so can be modelled as a game theoretic problem. Our task, then, is to
determine control rules which lead to stable coordination across the team. Similarly, we can model
consider modelling a controller and an adversarial environment as a zero-sum game as examined in
\cite{Marden2018AnnualControl}.

Another application is proposed by Letcher et al in \cite{Letcher2019DifferentiableMechanics} - that
of Generative adversarial networks (GANs) which can be considered as a two player minimax game with
differentiable loss functions. As pointed out by Mylvaganam, it may also be interesting to consider
the differential game problem from the point of view of different information structures. In
real-world systems, it is unlikely that all agents will have access to the information of other
agent' cost functions and current positions. It could, however, be interesting to explore the use of
localisation methods to determine and track this information through observation (e.g. through
Kalman or Bayesian methods). Finally, most of the relevant work in stochastic optimal control
considers the case where system dynamics are linear. A whole new set of problems arise in the more
realistic case where we must consider the non-linearity of system dynamics. Such a consideration
would also allow us to extend these technique to the more difficult (and important) problems in
control.

The following papers \cite{Bailey2019FiniteDescent-Ascent, Bailey2019Multi-AgentSystem,
Boone2019FromTheory, DickensTheLearning, Berkenkamp2017SafeGuarantees,
Jin2018Stability-certifiedPerspective, Letcher2019DifferentiableMechanics} are the ones that I found
particularly relevant to this study. However, they will require some further analysis before I write
about them here. (Note: I've written about some of these in the paragraphs above, but I'm not
entirely sure which ones yet. I think the job over Christmas will mainly be about sorting this
document out.)

\chapter{Research Directions}

\section{Stochastic Model Predictive Control for Distributed Systems}

The work on distributed stochastic MPC (DSMPC) is still rather sparse but is advancing rapidly. To
that end, I propose the following techniques towards improving DSMPC.

>>>>

Reinforcement learning extends the Markov Decision Process problem by considering the case where the
reward model is not initially known to the agent. In a similar manner, Multi Agent Reinforcement
Learning (MARL) extends the Markov Game setting to one where the payoff structure is not a priori
knowledge.

The task of MARL is to determine an optimal joint policy for all agents across the game. This joint
policy may be the concatenation of all the individual policy or it may just be options for each
agent to take. In either case, optimality is defined through the standard notions of Nash equilibria
and so, in this section, I will try to consider the broad spectrum of methods which attempt to
achieve this Nash equilibria. The largest problem in MARL is the non-stationarity of the environment
\cite{Hernandez-LealA}. In single-agent settings, it is assumed that the environment is Markovian.
However, this must be lifted in the Multi Agent setting since other agents in the environment will
be learning concurrently. As such, we must now consider that the policy for any one agent will
depend on the policy of all other agents.

This chapter begins with a selection of the foundational methods which were developed towards
solving the MARL problem. The interested reader may find a stronger review and analysis in
\cite{SchwartzMulti-agentApproach}. I then go on to consider more contemporary approaches, most
notably that of agent modelling.

\section{Learning in Two Player Matrix Games}

\section{Learning in Multiplayer Stochastic Games}

\TODO{Consider the case for partially observed/decentralised settings. Find the relevant material
within \cite{SchwartzMulti-agentApproach} which addresses this issue.}

@@

@@

\section{Stable Learning}

This section considers a dynamical systems approach towards learning agents. Its aim is to develop learning systems which prioritise stability.

@@

\TODO{In the above, look specifically at the assumptions made within the papers. In the multi-agent
case, the biggest assumption is that of independent learning. Perhaps consider how advances in
coupled dynamical systems may be used to consider learning agents whose actions affect one another.}
